Association Rules
========================================================
## Basics of Association Rules
support$(A \Rightarrow B)$=$P(A \cup B)$

confidence$(A \Rightarrow B)$=$P(A | B)$

lift$(A \Rightarrow B)$=confidence$(A \Rightarrow B)$/$P(B)$
##  The Titanic Dataset
The `Titanic` dataset in the *datasets* package is a 4-dimensional table with summarized information
on the fate of passengers on the Titanic according to social class, sex, age and survival.

```{r}
str(Titanic)
(df <- as.data.frame(Titanic))
```

* 第1列表示 1st class 中的男性孩童死了0人 and so on.
* 第17列表示 1st class 中的男性孩童存活5人 and so on.

We reconstruct the raw data as `titanic.raw`, where **each row
represents a person**. 

```{r}
titanic.raw <- NULL
for(i in 1:4) {
titanic.raw <- cbind(titanic.raw, rep(as.character(df[,i]), df$Freq))
}
titanic.raw <- as.data.frame(titanic.raw)
names(titanic.raw) <- names(df)[1:4]
str(titanic.raw)
head(titanic.raw)
summary(titanic.raw)
```

## Association Rule Mining
```{r,message=FALSE}
library(arules)
rules.all <- apriori(titanic.raw,
                     control=list(verbose=FALSE), ## 不要 show 過程
                     parameter = list(minlen=2 , supp=0.005, conf=0.8), ##(the minimal number of items per item set ,  the minimal surpport, the minimal confidence)
                     appearance = list(rhs=c("Survived=No", "Survived=Yes"),
                                       default="lhs")) ## (set item for right hand side, the default appearance for all items not explicitly mentioned in the other elements of the list.)
quality(rules.all) <- round(quality(rules.all), digits=3)
rules.sorted <- sort(rules.all, by="lift")
inspect(rules.sorted)
```

## Removing Redundancy

在有了 rule 1 之後, rule 2 並不能提供更多訊息, we call rule 2 is a super rule of rule 1.
The following code find and delete all super rule.

```{r}
subset.matrix <- is.subset(rules.sorted, rules.sorted)
redundant <- colSums(subset.matrix, na.rm=T) > 1
which(redundant)
rules.pruned <- rules.sorted[!redundant]
inspect(rules.pruned)
```

## Interpreting Rules

只想知道 `Class` 與 `Age` 與 `survived=Yes`
的關係
```{r}
rules <- apriori(titanic.raw,
parameter = list(minlen=3, supp=0.002, conf=0.2),
appearance = list(rhs=c("Survived=Yes"),
lhs=c("Class=1st", "Class=2nd", "Class=3rd",
"Age=Child", "Age=Adult"),
default="none"),
control = list(verbose=F))
rules.sorted <- sort(rules, by="confidence")
inspect(rules.sorted)
```

* High survival rate for child in 1st class and 2nd class, but not in 3rd class
* 3rd class has lowest survival rate no matter child or adult.  

## Visualizing Association Rules
```{r,message=FALSE}
library(arulesViz)
plot(rules, method="graph", control=list(type="items"))
```